---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)

library(magrittr)
```

# lilsebastian

<!-- badges: start -->
[![lifecycle](https://img.shields.io/badge/lifecycle-experimental-brightgreen.svg)](https://www.tidyverse.org/lifecycle/#experimental)
<!-- badges: end -->

Explore the inner workings of the Pawnee Parks and Recreation Department.

## Installation

You can install the development version of lilsebastian from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("corysauve/lilsebastian")
```
## Basic Usage 

lilsebastian contains the entire transcript for *Parks and Recreation*, organized by season and episode:
```{r}
library(lilsebastian)

dplyr::glimpse(parksandrec)
```

## Contributing 

I welcome any contributions or suggestions for improving this package! Please open an issue to do so. 

## License 

The lilsebastian package is licensed under the MIT License. Please see the [LICENSE](LICENSE.md) for more details.
